Summary Tables ITHIMR

### 2020-09-03 summary_tables_PA_AP.Rmd
Get city names from ithim object, and replace 'bicycle' with 'cycle'

cities <- c("accra", "sao_paulo", "delhi", "bangalore")
high<- c(70, 25, 150,60)
low<- c(40,15,100,40)
for (x in 1: length(cities))
{

@@

  summary<- as.data.frame(io[[cities[x]]]$outcomes$injuries %>% group_by(scenario) %>% summarise('Ped'=sum(pedestrian,na.rm=T),'Bike'= sum(bicycle), 'Car'=sum(car), "Motorcycle"=sum(motorcycle,na.rm=T), "All modes"=sum(Deaths,na.rm=T)))
  summary$scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  summary<- cbind(summary$scenario ,round(summary[,2:6], digits=0))
  names(summary)[1]<-"Scenario"
  print(kable(summary, caption= cities[x]))

@@

  select<- c("car", "motorcycle", "walking", "bicycle", "bus")

>>>>

# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']
high<- c(70, 25, 150,60)
low<- c(40,15,100,40)
for (x in 1: length(cities))
{

@@

  summary<- as.data.frame(io[[cities[x]]]$outcomes$injuries %>% group_by(scenario) %>% summarise('Ped'=sum(pedestrian,na.rm=T),'Bike'= sum(cycle), 'Car'=sum(car), "Motorcycle"=sum(motorcycle,na.rm=T), "All modes"=sum(Deaths,na.rm=T)))
  summary$scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  summary<- cbind(summary$scenario ,round(summary[,2:6], digits=0))
  names(summary)[1]<-"Scenario"
  print(kable(summary, caption= cities[x]))

@@

  select<- c("car", "motorcycle", "walking", "cycle", "bus")
